Arbitrary Precision and Arbitrary $n$-Grams

### 2011-03-01 paper/paper.Rnw
spellcheck

For each combination of the intependent variables, we
generated 23 sentences from the \emph{War and Peace} corpus
and tested their perplexity. We did the same the Shakespeare corpus
but generated only 7 sentences for each treatment combination.

@@

\subsection*{Pelplexity of test set}
For each corpus, perplexity of test set decreased when the models
were run for longer $n$-grams, and the perplexity
leveled off starting at $n=3$ (figure \ref{fig:test}). Probability computation type had no effect.

>>>>

For each combination of the independent variables, we
generated 23 sentences from the \emph{War and Peace} corpus
and tested their perplexity. We did the same the Shakespeare corpus
but generated only 7 sentences for each treatment combination.

@@

\subsection*{Perplexity of test set}
For each corpus, perplexity of test set decreased when the models
were run for longer $n$-grams, and the perplexity
leveled off starting at $n=3$ (figure \ref{fig:test}). Probability computation type had no effect.
